---
title: "Atlas de Buceo de México"
resource_files:
- "shp/Diving_sites_v1.0_01032021/dive_sites.shx"
- "shp/Diving_sites_v1.0_01032021/dive_sites.prj"
- "shp/Diving_sites_v1.0_01032021/dive_sites.dbf"
- "shp/Diving_sites_v1.0_01032021/dive_sites.cpg"
- "shp/Tourism_operators_v1.0_01032021/operators.cpg"
- "shp/Tourism_operators_v1.0_01032021/operators.dbf"
- "shp/Tourism_operators_v1.0_01032021/operators.prj"
- "shp/Tourism_operators_v1.0_01032021/operators.qpj"
- "shp/Tourism_operators_v1.0_01032021/operators.shx"
- "shp/MPA_MX_v1.0_01032021/MPA_MX_c1-0.shx" 
- "shp/MPA_MX_v1.0_01032021/MPA_MX_c1-0.prj" 
- "shp/MPA_MX_v1.0_01032021/MPA_MX_c1-0.dbf" 

runtime: shiny
output:
        flexdashboard::flex_dashboard:
        source_code: embed
        theme: united
---
        
Atlas de Buceo de México
=======================================================================
        
```{r setup, include=FALSE}

library(flexdashboard)
library(leaflet)
library(mapview)
library(rgdal)
library(sf)
library(tidyverse)
library(ggthemes)


# Loading diving site data and diving operators data ----------------

ds <- raster::shapefile("shp/Diving_sites_v1.0_01032021/dive_sites.shp", verbose = FALSE)
to <- raster::shapefile("shp/Tourism_operators_v1.0_01032021/operators.shp", verbose = FALSE)

# Loading MPA layer -------------------
mpa <- raster::shapefile("shp/MPA_MX_v1.0_01032021/MPA_MX_c1-0.shp", encoding = "latin1")

```


```{r}

to$labels1 <- paste0("<strong> Región: </strong> ", to$region, "<br/> ",
                     "<strong> Estado: </strong> ", to$state, "<br/> ",
                     "<strong> Nombre: </strong> ", to$company_na, "<br/> ",
                     "<strong> Latitud: </strong> ", to$lat, "<br/> ",
                     "<strong> Longitud: </strong> ", to$LONG, "<br/> ",
                     "<strong> Dirección: </strong> ", to$long, "<br/> ",
                     "<strong> Telefono: </strong> ", to$phone, "<br/> ",
                     "<strong> Correo: </strong> ", to$email, "<br/> ") %>%
        lapply(htmltools::HTML)

ds$labels2 <- paste0("<strong> Nombre sitio: </strong> ", ds$site_name, "<br/> ",
                     "<strong> Región: </strong> ", ds$region, "<br/> ",
                     "<strong> Localidad: </strong> ", ds$locality, "<br/> ",
                     "<strong> Estado: </strong> ", ds$state, "<br/> ",
                     "<strong> Popularidad: </strong> ", ds$popularity, "<br/> ",
                     "<strong> Latitud: </strong> ", ds$latitude, "<br/> ",
                     "<strong> Longitud: </strong> ", ds$longitude, "<br/> ") %>%
        lapply(htmltools::HTML)


mpa$labels3 <- paste0("<strong> Name: </strong> ", mpa$ANP, "<br/> ",
                      "<strong> Plan de Manejo: </strong> ", mpa$PM_link, "<br/> ",
                      "<strong> Fecha: </strong> ", mpa$FECHA, "<br/> ",
                      "<strong> Zona: </strong> ", mpa$Categor, "<br/> ",
                      "<strong> Subzona </strong> ", mpa$Subznfc, "<br/> ",
                      "<strong> Buceo: </strong> ", mpa$Buceo, "<br/> ",
                      "<strong> Pesca: </strong> ", mpa$Pesca, "<br/> ") %>%
        lapply(htmltools::HTML)


icons <- awesomeIcons(
        icon = 'flag-outline',
        iconColor = 'black',
        library = 'ion')


leaflet(to) %>%
        addProviderTiles(providers$Esri.WorldImagery, group = "Satélite") %>%
        addProviderTiles(providers$Esri.WorldTopoMap, group = "Mapa") %>%
        addProviderTiles(providers$Esri.OceanBasemap, group = "Ocean") %>%

        setView(lng = -108, lat = 25, zoom = 2) %>%
        addAwesomeMarkers(
                popup = ~ labels1,
                group = "Operators",
                icon = awesomeIcons(icon = "home",
                                    markerColor = "darkred",
                                    library = "ion")
        ) %>%
        addPolygons(
                data = mpa,
                group = "AMPs",
                weight = 2,
                opacity = 1,
                fillColor = "red",
                fillOpacity = 0.1,
                color = "black",
               #dashArray = "3",
                highlightOptions = highlightOptions(
                        color = "white",
                        weight = 2,
                        bringToFront = TRUE
                ),
                popup = ~ labels3
        ) %>%
        addMarkers(
                data = ds, 
                group = "Diving sites",
                popup = ~ labels2
        ) %>% 
        # Layers control
        addLayersControl(
                baseGroups = c("Satélite", "Mapa", "Ocean"),
                overlayGroups = c("Operators", "AMPs", "Diving sites"),
                options = layersControlOptions(collapsed = TRUE)
        ) %>%
        hideGroup(c("Operators", "Diving sites")) %>%
        setView(lng = -99.1332,
                lat = 19.4326,
                zoom = 4)


```




Credits
=======================================================================
        
### About the project

This work is part of the diving atlas initiative in Mexico, a project where international institutions are collaborating: the Scripps Institution of Oceanography (USA), the Gulf of California Marina Program (USA), the Centro para la Biodiversidad Marina y la Conservación, A.C. (México), the Universidad Autónoma de Baja California Sur (México), the Senckenberg Institute (Germany). 

### Data sources

- Mexican MPA layer is currently under development, original data from: http://sig.conanp.gob.mx/website/pagsig/info_shape.htm


### Dashboard, data creation and supervision: 

- Dr. Fabio Favoretto (UABCS-CBMC);

### Data creation:

- Joy Kumagai (Senckenberg);
- Terrance Wang (NOAA);
- Norman Blanco Lupio (CBMC);
- Eduardo León Solórzano (UABCS);
- Eduardo Peláez Torres (UABCS);

### Project supervision: 

- Marisol Placencia de la Cruz (CBMC); 
- Octavio Aburto Oropeza (SIO); 
- Catalina López Sagastégui (UC-Mexus);

